\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{geometry}

% Elegant Palatino font
\usepackage{mathpazo}
\linespread{1.05}

% Tight margins for single-page fit
\geometry{left=0.45in, top=0.38in, right=0.45in, bottom=0.35in}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Compact section heading
\titleformat{\section}{\bfseries\normalsize}{}{0em}{}[\vspace{-7pt}\hrulefill\vspace{-2pt}]
\titlespacing{\section}{0pt}{6pt}{4pt}

\pdfgentounicode=1

\begin{document}

%=== HEADER ===
\begin{center}
    {\LARGE \bfseries Nithin E} \\[2pt]
    {\normalsize \bfseries Data Scientist} \\[3pt]
    \small
    +91 7538866807 $|$
    \href{mailto:nithinx002@gmail.com}{nithinx002@gmail.com} $|$
    \href{https://www.linkedin.com/in/nithin-devigner}{LinkedIn} $|$
    \href{https://github.com/codemonkx}{GitHub} $|$
    Bengaluru, Karnataka
\end{center}
\vspace{-2pt}
\hrule
\vspace{4pt}

%=== SUMMARY ===
\section*{Summary}
I am an AI \& Data Science graduate who loves turning complex problems into working applications. Through building projects like an autonomous cybersecurity agent and a brain tumor detection model, I've gained solid, hands-on experience with Python, machine learning frameworks, and databases. My focus is on leveraging these tools to build robust, end-to-end AI solutions that deliver real-world impact.

\vspace{2pt}

%=== TECHNICAL SKILLS ===
\section*{Technical Skills}
\begin{itemize}[leftmargin=*, noitemsep, topsep=1pt]
    \item \textbf{Programming \& Analytics:} Python (Pandas, NumPy, Matplotlib, Seaborn, Scikit-learn, PyTorch, TensorFlow, Keras), SQL
    \item \textbf{AI/ML Frameworks:} TensorFlow, Keras, PyTorch, Scikit-learn, LangGraph, LLM APIs (Groq Llama, Mistral), GNN, Isolation Forest
    \item \textbf{Database Systems:} MySQL, MongoDB
    \item \textbf{Tools \& Platforms:} Jupyter Notebook, VS Code, Git/GitHub, Power BI Service
\end{itemize}

\vspace{2pt}

%=== PROJECTS ===
\section*{Projects}

\noindent
\textbf{AI-Powered Cyber Defense System (Project Defend)}
\hfill \href{https://github.com/codemonkx/Server-Defence-System}{\textit{GitHub}}\\[-2pt]
\textit{\small React, Node.js, Python, GNN, PyTorch, LangGraph, LLMs (Groq Llama, Mistral)}
\begin{itemize}[leftmargin=*, noitemsep, topsep=1pt]
    \item Developed a MERN-based E-learning platform integrated with an autonomous AI defense agent for real-time threat mitigation.
    \item Engineered a multi-model anomaly detection system using \textbf{GNNs}, \textbf{Isolation Forests}, and OC-SVM to dynamically block DoS, XSS, and SQLi attacks.
    \item Designed explainable agentic workflows with \textbf{LangGraph} and LLMs to automate IP firewalling and generate live security telemetry.
\end{itemize}

\vspace{2pt}

\noindent
\textbf{Brain Tumor Detection Model}
\hfill \href{https://github.com/codemonkx/Brain-Tumor-prediction}{\textit{GitHub}}\\[-2pt]
\textit{\small Python, Scikit-learn, TensorFlow, Keras, Pandas}
\begin{itemize}[leftmargin=*, noitemsep, topsep=1pt]
    \item Developed a machine learning pipeline to classify tumors as malignant or benign based on cellular features, achieving \textbf{92.00\% accuracy}.
    \item Engineered robust data processing workflows for feature extraction, analyzing nucleus size, texture, perimeter, and compactness.
    \item Trained and evaluated \textbf{Random Forest} and Deep Learning models to optimize diagnostic performance for medical AI research.
\end{itemize}

\vspace{2pt}

\noindent
\textbf{PacTune — Desktop Music Player}
\hfill \href{https://github.com/codemonkx/PacTune}{\textit{GitHub}}\\[-2pt]
\textit{\small Rust, GTK4, Libadwaita, GStreamer, Relm4}
\begin{itemize}[leftmargin=*, noitemsep, topsep=1pt]
    \item Built a high-performance, native Linux desktop music player in \textbf{Rust} using \textbf{GTK4} and Libadwaita for seamless GNOME integration.
    \item Integrated \textbf{GStreamer} for multi-format audio playback and engineered an automated, auto-syncing lyrics fetcher (.lrc support).
    \item Designed a reactive UI with Relm4, featuring album artwork grids, media key support, and automated installation scripts.
\end{itemize}

\vspace{2pt}

%=== CERTIFICATIONS ===
\section*{Certifications}
\begin{itemize}[leftmargin=*, noitemsep, topsep=1pt]
    \item \textbf{Data Analyst Course — PYSpiders} \textit{(2024)}: Python, Power BI, and SQL.
    \item \textbf{Data Science Course — Udemy} \textit{(2024)}: ML, Statistics, Python, and Power BI with real-world projects.
\end{itemize}

\vspace{2pt}

%=== EDUCATION ===
\section*{Education}
\begin{tabularx}{\textwidth}{@{}X r@{}}
    \textbf{B.Tech in Artificial Intelligence \& Data Science} $|$ CGPA: \textbf{7.2/10} & \textbf{2026} \\
    \textit{Mahendra Engineering College, Tamil Nadu} & \\
    \small \textit{Relevant Coursework: Probability \& Statistics, Machine Learning, Deep Learning, Data Structures} & \\
\end{tabularx}

\end{document}
